Isomorphic Interpreters from Logically Reversible Abstract Machines

### 2012-03-15 iso-int/rc-iso-int.tex
Pi

\item Commutativity is represented by crisscrossing wires.
\begin{multicols}{4}
\begin{center}
\scalebox{0.95}{
%%subcode-line{pdfimage}[diagrams/thesis/swap-pair.pdf]
\includegraphics{diagrams/thesis/swap_times.pdf}
}
\end{center}
%% \end{multicols}
%% \begin{multicols}{2}
\begin{center}
\scalebox{0.95}{
\includegraphics{diagrams/thesis/swap_times_value.pdf}
}
\end{center}

@@

By visually tracking the flow of particles on the wires, one can
verify that the expected types for commutativity are satisfied.

@@

\item Distributivity and factoring are represented using the dual
  boxes shown below:
\begin{multicols}{4}
\begin{center}
  \includegraphics{diagrams/thesis/dist.pdf}
\end{center}
\begin{center}
  \includegraphics{diagrams/thesis/factor.pdf}
\end{center}
%% \end{multicols}
%% \begin{multicols}{2}
\begin{center}
  \includegraphics{diagrams/thesis/dist-wire-value1.pdf}
\end{center}
\begin{center}
  \includegraphics{diagrams/thesis/dist-wire-value2.pdf}
\end{center}
\end{multicols}

Distributivity and factoring are interesting because they represent
interactions between sum and pair types. Distributivity should
essentially be thought of as a multiplexer that redirects the flow of
{{v:b}} depending on what value inhabits the type {{b1+b2}}, as shown
below. Factoring is the corresponding adjoint operation.

>>>>

\item Commutativity is represented by crisscrossing wires.  By
  visually tracking the flow of particles on the wires, one can verify
  that the expected types for commutativity are satisfied.

\begin{multicols}{4}
\begin{center}
\scalebox{0.95}{
%%subcode-line{pdfimage}[diagrams/thesis/swap-pair.pdf]
\includegraphics{diagrams/thesis/swap_times.pdf}
}
\end{center}
%% \end{multicols}
%% \begin{multicols}{2}
\begin{center}
\scalebox{0.95}{
\includegraphics{diagrams/thesis/swap_times_value.pdf}
}
\end{center}

@@

@@

\item Distributivity and factoring are interesting because they
  represent interactions between sum and pair types. Distributivity
  should essentially be thought of as a multiplexer that redirects the
  flow of {{v:b}} depending on what value inhabits the type {{b1+b2}},
  as shown below. Factoring is the corresponding adjoint operation.

\begin{multicols}{4}
\begin{center}
  \includegraphics{diagrams/thesis/dist.pdf}
\end{center}
\begin{center}
  \includegraphics{diagrams/thesis/factor.pdf}
\end{center}
%% \end{multicols}
%% \begin{multicols}{2}
\begin{center}
  \includegraphics{diagrams/thesis/dist-wire-value1.pdf}
\end{center}
\begin{center}
  \includegraphics{diagrams/thesis/dist-wire-value2.pdf}
\end{center}
\end{multicols}
